Methods for Projecting Population Growth

### 2018-05-08 final/tex/Paper.tex
Add figures

@@

%\begin{figure}[ht!]
%\centering
%\includegraphics[width=90mm]{images/lr-graph.png}
%\caption{Results of using least squares on logistic growth \label{overflow}}
%\end{figure}

@@

@@

@@

>>>>

\todo{Fix figure captions}

\todo{Add figure labels/references}

@@

@@

\begin{figure}[ht!]
\includegraphics[width=80mm]{images/world-pop.png}
\includegraphics[width=80mm]{images/world-gdp.png}
\caption{Results of modeling world population and GDP by manual modifications based off of minimizing scoring function \label{overflow}}
\end{figure}

@@

\begin{figure}[ht!]
\includegraphics[width=80mm]{images/us-pop.png}
\includegraphics[width=80mm]{images/us-gdp.png}
\caption{Results of modeling U.S. population and GDP by using the least squares method\label{overflow}}
\end{figure}

@@

\begin{figure}[ht!]
\includegraphics[width=80mm]{images/sa-pop.png}
\includegraphics[width=80mm]{images/sa-gdp.png}
\caption{Results of modeling South Africa population and GDP by using the least square method.  \label{overflow}}
\end{figure}
